An upper bound to gas storage and delivery via pressure-swing adsorption in porous materials

### 2021-02-25 gas-adsorption/referee-response.md

## Response to referees

# Referee 1

Referee 1 states that "Phenomenological predictions without any relation to real
materials are not very helpful, if not useless."  The referee fails to grasp
that our theory *does* take into account the gas, and places a fundamental limit
on the capacity of an entire class of materials (inflexible porous materials).
This is far from useless.  The referee suggests as superior an approach
involving screening hundreds of thousands of actual MOFs.  We will point out
that such an approach cannot possibly determine that there isn't a better MOF
out there, while our approach can do so.

TODO: We should find a place to edit the paper to make this more clear, and
state here that we did so.

TODO: Maybe include some more discussion of pore volume, just to illustrate that
our method does give information related to things like pore volume?

The other suggestion of Referee 1 is that we clearly state the capacity that we report, as discussed by Parilla et al.

TODO: We must do so.

# Referee 3

Referee 3 states that the conclusions are convincing, and makes two suggestions
for improving the paper:

1. The referee suggests that we attempt to quantify the possible effect of a
   flexible MOF on our upper bound.

TODO: Add a bit of discussion of how and why our model does not apply to
flexible MOFs, and why we cannot place *any* upper bound on a flexible MOF using
our approach.

2. The referee asks that we provide some guidelines in terms of working
   conditions to reach the DOE target.  They further suggest looking at a
   temperature difference to see how that could impact the deliverable capacity.

TODO: Add *some* sort of extra discussion on the topic.  Our model cannot
predict a temperature+pressure swing cycle because that would require
information about the entropy of adsorption at the two temperatures, which is
rather trickier, I think.

### 2021-02-25 gas-adsorption/referee-response.md

## Response to referees

Dear editor,

The responses of referees 1 and 3 could hardly be more divergent.  We FIXME
SHOULD ADD A SUCCINCT ARGUMENT HERE WHY REFEREE 3 IS BETTER.

@@

# Referee 1

Referee 1 states that "Phenomenological predictions without any relation to real
materials are not very helpful, if not useless."  The referee fails to grasp
that our theory *does* take into account the gas, and places a fundamental limit
on the capacity of an entire class of materials (inflexible porous materials).
This is far from useless.  The referee suggests as superior an approach
involving screening hundreds of thousands of actual MOFs.  We will point out
that such an approach cannot possibly determine that there isn't a better MOF
out there, while our approach can do so.

TODO: We should find a place to edit the paper to make this more clear, and
state here that we did so.

The referee gives a litany of structural properties that we do not address in
our model: "pore volume, pore size, specific surface area, crystal density,
skeletal density, packing density, different adsorption sites etc."

    We note that some of these (e.g. crystal density, skeletal density)
    manifestly have no impact on the property we are studying, which is
    volumetric storage capacity.  Others of course do impact the volumetric
    storage capacity of a material, but do not relate to an upper bound
    specifically.  TODO: We do add a discussion of the pore volume fraction
    and how it can constrained by our upper bound, to make more clear the
    range of applications of our bound.  TODO: We can put a lower bound on
    pore volume fraction contingent on the maximum density having a given value.
    It will take some explanation, but I think is worthwhile.

### 2021-03-05 gas-adsorption/rsc-gas-ads-complete.tex
start flexible thingy

To show that a uniform potential gives the highest deliverable capacity, we
consider an interaction potential between gas and substrate offering a
potential energy field $\V(\rvec)$ that varies in space. We will show that the
uniform potential has the highest deliverable capacify of the set of potentials
having the same mean value, and to find the maximum deliverable capacity one
maximizes over this mean value. In this proof, we make use of the Fourier
transform of this potential:
\begin{align}
    \Vk \equiv \iiint \V(\rvec) e^{-i\kvec\cdot \rvec} d\rvec
\end{align}
The Fourier transform of a uniform potential is a Dirac delta function
$\tilde{\V}(\kvec)\propto\delta(\kvec)$. For a uniform potential to extremize
the deliverable capacity, we must show that the functional derivative of the
deliverable capacity with respect to $\Vk$ is zero for \emph{nonzero} values of
$\kvec$, i.e.
\begin{align}
    \frac{\delta \rho_D}{\delta \Vk} &= \mathbf{0}, \text{ if } \kvec\ne \mathbf{0}.
\end{align}
We note that this functional derivative may be non-zero for $\kvec=\mathbf{0}$
because we separately maximize with respect to the mean value of the uniform
potential $\V$. This means that
\begin{align}
    \frac{\delta N_\text{full}}{\delta \Vk} &= \frac{\delta N_\text{empty}}{\delta \Vk}
\end{align}
where $N_\text{full}$ and $N_\text{empty}$ are the number of particles in the
substrate at the full and empty pressure, $\pfull$ and $\pempty$, respectively.

@@

>>>>

To show that a uniform potential gives the highest deliverable capacity, we
consider an interaction potential between gas and substrate offering a
potential energy field $\V(\rvec)$ that varies in space. We will show that the
uniform potential has the highest deliverable capacity of the set of potentials
having the same mean value, and to find the maximum deliverable capacity one
maximizes over this mean value. In this proof, we make use of the Fourier
transform of this potential:
\begin{align}
    \Vk \equiv \iiint \V(\rvec) e^{-i\kvec\cdot \rvec} d\rvec
\end{align}
The Fourier transform of a uniform potential is a Dirac delta function
$\tilde{\V}(\kvec)\propto\delta(\kvec)$. For a uniform potential to extremize
the deliverable capacity, we must show that the functional derivative of the
deliverable capacity with respect to $\Vk$ is zero for \emph{nonzero} values of
$\kvec$, i.e.
\begin{align}
    \frac{\delta \rho_D}{\delta \Vk} &= \mathbf{0}, \text{ if } \kvec\ne \mathbf{0}.
\end{align}
We note that this functional derivative may be non-zero for $\kvec=\mathbf{0}$
because we separately maximize with respect to the mean value of the uniform
potential $\V$. This means that
\begin{align}
    \frac{\delta N_\text{full}}{\delta \Vk} &= \frac{\delta N_\text{empty}}{\delta \Vk}
\end{align}
where $N_\text{full}$ and $N_\text{empty}$ are the number of particles in the
substrate at the full and empty pressure, $\pfull$ and $\pempty$, respectively.

@@

\section{Flexible two-state model}

\begin{align}
    |n(p_{hi})\V| &> |\Delta F| \\
    |n(p_{lo})\V| &< |\Delta F|
\end{align}
This means that for a given $\Delta F$ we can put an upper bound on the
deliverable capacity.
